### 2017-11-01 1/exams/m2-practice.tex
Fix bug.

\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{times}
\usepackage{xcolor,censor}
\usepackage{fancyvrb}

@@

\begin{SaveVerbatim}{VerbEnv}
SOLUTION:

(define (f b s) s)
(define (g fs) (fs #false))
(define (h bs ns) 2)
(define (i f) (f 2))
(define (j xs) (map f xs))
(define (k f g x) (g (f x)))
\end{SaveVerbatim}

@@

\begin{verbatim}
;; f : \censor{Number -> Number}

@@

(define (k x y)
  (cond [(= y 0) (list (x 0))]
        [else
          (cons (x y) (k x (sub1 y)))]))
\end{verbatim}

@@

\begin{SaveVerbatim}{VerbEnv}
SOLUTION:

@@

\begin{SaveVerbatim}{VerbEnv}
SOLUTION:

;; most-games : Tournament -> Number
;; Compute most games any team has to win to win tournament
(check-expect (most-games "NY") 0)
(check-expect (most-games (make-bracket "LA" "HOU")) 1)
(check-expect (most-games (make-bracket (make-bracket "LA" "DC") "HOU")) 2)
(define (most-games t)
  (cond [(string? t) 0]
        [(bracket? t)
         (add1 (max (most-games(bracket-t1 t))
                    (most-games(bracket-t2 t))))]))
\end{SaveVerbatim}

>>>>

\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{xcolor,censor}
\usepackage{fancyvrb}
\usepackage{fontspec}
\usepackage{alltt}

\setmainfont{Times New Roman}

@@

\begin{SaveVerbatim}{VerbEnv}

SOLUTION:

(define (f b s) s)
(define (g fs) (fs #false))
(define (h bs ns) 2)
(define (i f) (f 2))
(define (j f xs) (map f xs))
(define (k f g x) (g (f x)))
\end{SaveVerbatim}

@@

\begin{alltt}
;; f : \censor{Number -> Number}

@@

(define (k x y)
  (cond [(= y 0) (list (x 0))]
        [else
          (cons (x y) (k x (sub1 y)))]))
\end{alltt}

@@

\begin{SaveVerbatim}{VerbEnv}

SOLUTION:

@@

\begin{SaveVerbatim}{VerbEnv}

SOLUTION:

;; most-games : Tournament -> Number
;; Compute most games any team has to win to win tournament
(check-expect (most-games "NY") 0)
(check-expect (most-games (make-bracket "LA" "HOU")) 1)
(check-expect (most-games (make-bracket (make-bracket "LA" "DC") "HOU")) 2)
(define (most-games t)
  (cond [(string? t) 0]
        [(bracket? t)
         (add1 (max (most-games (bracket-t1 t))
                    (most-games (bracket-t2 t))))]))
\end{SaveVerbatim}
